\plaintitle

### 2016-09-20 drafts/labor/complexity.tex
fix ref in complexity

\msb{this doesn't seem like a concrete prediction. what would piecework say will happen if we didn't resolve the tension?}
We should also consider exploring the limitations that algorithmic management bring along more carefully.
While research has touched on this subject, we've yet to make out the bigger picture of this theme
\cite{uberAlgorithm}.
If we can resolve the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest,
then we may be able to break a toxic cycle of mistrustful requesters \cite[for example][]{MaliciouscrowdworkersGadiraju}
and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
\cite{takingAHITMcInnis}.

>>>>

\msb{this doesn't seem like a concrete prediction. what would piecework say will happen if we didn't resolve the tension?}
We should also consider exploring the limitations that algorithmic management bring along more carefully.
While research has touched on this subject, we've yet to make out the bigger picture of this theme
\cite{uberAlgorithm}.
If we can resolve the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest,
then we may be able to break a toxic cycle of mistrustful requesters \cite[for example][]{MaliciousCrowdworkersGadiraju}
and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
\cite{takingAHITMcInnis}.
